### 2021-12-04 paper/manuscript.Rmd
update 2021-12-04 11:46:32

---
title             : "Select relevant moderators in meta-regression using Bayesian penalization"
shorttitle        : "Title"

author:
  - name: "Caspar J. Van Lissa"
    affiliation: "1,2"
    corresponding: yes
    address: "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email: "c.j.vanlissa@uu.nl"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing    
  - name: "Andreas M. Brandmaier"
    affiliation: "3,4"

  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

@@

Skeleton lasso/pema paper
1.) What is Meta-analysis?
2.) What is meta-regression and how does it complement meta-analysis?
	a.) Introduce Moderators
	b.) Study Heterogeneity + Random Sampling Error (and their difference)	
2.5.) Fixed vs. random effects
	a.) Shortcomings of fixed effect models
3.) Shortcomings of current meta regressions w.r.t. estimating coefficients and heterogeneity:
	a.) Small sample size / overfitting
	b.) Non-normal data
4.) Various methods to estimate heterogeneity (and coefficients)
	a.) The use of WLS and REML
5.) Intro to Frequentist linear methods/Bayesian methods and Random forests, along with their 
(dis-)advantages:
	a.) Rma: uses WLS for estimation
	b.) MetaForest (Random Effects): Uses Random Forest Algorithm
	c.) Lasso Pema: uses penalized Lasso
	d.) Horseshoe Pema: uses horseshoe priors
6.) Goal of the current study
7.) Means of attaining goal and evaluation of performance:
	a.) simulation study
	b.) algorithmic performance
	c.) design factors
	d.) Impact of design factors on algorithim performance
	e.) Hypotheses of algorithmic performances

@@

# Introduction

Meta-analysis is the practice of aggregating effect sizes from multiple similar studies.
In its simplest form, a summary effect is computed as a weighted average of the observed effect sizes. 
The weight assigned to each effect size is based on certain assumptions,
and determines how influential it is in calculating the summary effect.
For example, the *fixed effect* model assumes that all observed effect sizes reflect one underlying true population effect size.
This assumption may be reasonable for close replication studies [@higgins_re-evaluation_2009, fabrigar_conceptualizing_2016, maxwell_is_2015]. 
The *random effects* model, by contrast, assumes that population effect sizes follow a normal distribution.
Each observed effect size provides information about the mean and standard deviation of this distribution of population effect sizes.
This assumption is appropriate when studies are conceptually similar and differences between them are random [@higgins_re-evaluation_2009, fabrigar_conceptualizing_2016, maxwell_is_2015].

Aside from random heterogeneity in effect sizes, quantifiable between-study differences may introduce systematic heterogeneity.
Such between-study differences are known as "moderators".
For example, if studies have been replicated in Europe and the Americas, this difference can be captured by a binary moderator called "continent".
Alternatively, if studies have used different dosages of the same drug, this may be captured by a continuous moderator called "dosage".
Systematic heterogeneity in the observed effect sizes can be accounted for using *meta-regression* (Viechtbauer \& López-López, 2015).
This technique provides estimates of the effect of one or more study characteristics on the overall effect size,
as well as of the overall effect size and residual heterogeneity after controlling for their influence.

In applied research, meta-analysis is often used to summarize existing bodies of literature.
In such situations, the number of moderators is often relatively high because similar research questions have been studied in different laboratories,
using different methods, instruments, and samples.
Each of these between-study differences could be coded as a moderator, and some of these moderators may explain systematic heterogeneity.

It is theoretically possible to account for the influence of multiple moderators using meta-regression.
However, like any regression-based approach, meta-regression requires a relatively high number of cases (studies) per parameter obtain sufficient power to examine heterogeneity.
In practice the number of available studies is often low (Riley, Higgins, & Deeks, 2011).
This necessitates *variable selection*: the selection of a smaller subset of relevant moderators from a larger number of candidate moderators.

One way to perform variable selection is by relying on theory.
However, theories at the individual level of analysis do not necessarily generalize to the study level of analysis.
Using theories at the individual level for moderator selection at the study level amounts to committing the ecological fallacy: generalizing inferences across levels of analysis [@jargowskyEcologicalFallacy2004].
The so-called *decline effect* illustrates this problem.
It is a phenomenon whereby effect sizes in a particular tranche of the literature seem to diminish over time [@schoolerUnpublishedResultsHide2011].
The decline effect has been attributed to i.a. regression to the mean:
A finding initially draws attention from the research community because an anomalously large effect size has been published, and subsequent replications find smaller effect sizes.
The decline effect would cause the variable "year of publication" to be a relevant moderator of effect size - even if it is orthogonal to the outcome of interest within each study.
<!--A second example that might illustrate this problem is a study that concluded that American college students' empathy had decreased over time, based on meta-analysis of 72 samples collected between 1979 and 2009.-->

An alternative solution is to rely on statistical methods for variable selection [see @hastieElementsStatisticalLearning2009].
This paper introduces *penalized meta-regression* (implemented in the R-package `pema`),
an algorithm that performs variable selection by shrinking the regression weight for irrelevant moderators towards zero.
<!--
Thus, there is a need of a regularization method to curtail overfitting. Least Absolute Shrinkage and Selection Operator [LASSO] (L1-norm regularization) can fulfill this role, since it has an advantage in terms of feature selection. The goal of this project is to implement L1-norm regularization in the weighted meta-regression, developing an new estimator for penalized meta-regression.
This dilemma could be resolved by an exploratory technique that can identify relevant moderators in meta-analysis,
and which is relatively robust to small sample sizes.
-->

@@

To understand how the proposed `pema` algorithm estimates the relevant parameters and performs variable selection, it is instructional to first review the statistical underpinnings of the aforementioned classic approaches to meta-analysis.
First is the fixed-effect model, which assumes that each observed effect size $T_i$ is an estimate of an underlying true effect size $\Theta$ [@hedgesFixedRandomeffectsModels1998].
The only cause of variability in observed effect sizes is presumed to be effect size-specific sampling variance $v_i$.
Thus, for a collection of $k$ studies, the observed effects sizes of individual studies $i$ (for $i$ = 1,2, . . . $k$) are given by:

@@

Typically, the variance $v_i$ is treated as known, and computed as the square of the standard error of the effect size.
<!--
\begin{aligned}
y_i &= \theta_i + \epsilon_i &\text{where } \epsilon_i \sim N(0, \sigma^2_i)\\ % \text{ and } 
%\theta_1 &= \theta_2 \dots = \theta_k
\end{aligned}-->
Under the fixed effect model, the estimated population effect size  $\hat{\theta}$ is obtained by computing a weighted average of the observed effect sizes.
If sampling error is assumed to be the only source of variance in observed effect size,
then it follows that studies with smaller standard errors estimate the underlying true effect size more precisely<!--(Schmidt, Oh \& Hayes, 2009)-->.
The fixed-effect weights are thus simply the reciprocal of the sampling variance, $w_{i} =  \frac{1}{v_i}$.
The weigted average is then:

$$
\hat{\theta} = \frac{\sum_{i=1}^k w_iT_i}{\sum_{i=1}^k w_i}
$$

<!--A highly likely consequence is that this will lead to a huge amount of possible moderators (Caserio, 2014). Caused by differences in for example cultures of research populations and used methods or instruments (Neuman, 2011). Even in replication studies there are sometimes moderators that are unanticipated (Kunert, 2016). This leads very often to an eventual poor performance of the fixed-effects meta-analysis model (Snijders, 2005). -->

The second model is the random-effects model. This approach makes an additional assumption, namely about the true effect sizes. Where the fixed-effect model treats the true effects as constants, the random-effect model assumes that the true effects are random and follow a distribution of their own (Hedges \& Vevea, 1998). This means that variation in the observed effects ($y_{i}$) in the random model incorporates not only the sampling error but also the variation of the true effect sizes $\tau^{2}$ between the studies. In the case of the random effect model the observed effect size of $y_{i}$ is, given by:

 $y_{i} = \theta_{i}+\varepsilon_{i}$ 						(3)

With $\varepsilon_{i} \sim \mathcal{N}(0,\,\sigma_{i})\,$ but, in this case $\theta_{i}$ on itself is given by:

 $theta_{i} = \mu + \zeta_{i}$						(4)

With $\mu$ being the mean of the distribution of the true effect sizes and $\zeta_{i} \sim \mathcal{N}(0,\,\tau^{2})\,$ with $\tau^2$ being the variance of the population of true effect sizes. It could also be explained as the variance between the individual studies. 
However, in the case of random-effects, the true effects also follow a distribution, so therefore the between study variance is also taken into account when composing the weights for the individual studies. The individual weights for the random-effect model are given by:

 $W_{i} =  \frac{1}{\sigma^2_{i} + \tau^{2}}$						(5)
In the case of the random-effect model, the within-study- and between-study variance is necessary for the calculation of the weights. It is important to note that in the calculation of the individual weights, an estimation of study heterogeneity is used $\tau^{2}$. While the sampling error is known for each individual study, the true effect heterogeneity $\tau^{2}$ remains unknown. Therefore, an estimation of the heterogeneity value needs to be made to effectively calculate the weights. This estimation of the between-study variance is thus represented by $\tau^{2}$.

$$
\begin{aligned}
y_i &= \theta_i + \epsilon_i &\text{where } \epsilon_i \sim N(0, \sigma^2_i)\\ % \text{ and } 
%\theta_1 &= \theta_2 \dots = \theta_k
\end{aligned}
$$

**Meta-regression**
In the case of fixed- and random-effect meta-analysis, the observed effects are treated as estimations of the underlying true effect. In meta-regression the observed effects are estimated by the including the moderators. In other words, the true effect is now replaced by the moderator effects. This is expressed with the following equation, where $\theta_{i}$ represents the underlying true effect, $x_{i}$ the moderators, $\beta_{i}$ the coefficients, with $p$ being the number of moderators:

$\theta_{i}=\beta_{0}+ \beta_{1}x_{1}+ \beta_{2}x_{2} + \ldots + \beta_{p}x_{p}+ \zeta_{i}$			(6)

When this is substituted in the original equation it will result in:

$y_{i}=\beta_{0}+ \beta_{1}x_{1}+ \beta_{2}x_{2} + \ldots + \beta_{p}x_{p}+ \zeta_{i} + \varepsilon_{i}$			(7)

The error term $\zeta_{i}$ captures the residual heterogeneity after accounting for the moderators. This term is still included because it is often the case that there still remains heterogeneity unexplained after accounting for the moderators (Thompson \& Sharp, 1999). In this model the moderator effects are treated as fixed and the residual heterogeneity as random. Therefore, it is referred to as a mixed-effect meta-regression analysis model, in short, ME-MRA (Viechtbauer \& López-López, 2015). To solve this ME-MRA model, both the residual heterogeneity and the moderator coefficients need to be estimated. An accurate estimation of the residual heterogeneity contributes to a better interpretation of the effect of the moderators (Panityakul, Bumrungsup \& Knapp, 2013).

**Estimating residual heterogeneity**
The topic of estimating the residual heterogeneity is a highly discussed one (Veroniki et al., 2016; Viechtbauer \& López-López, 2015; Panityakul et al., 2013). The ability of the estimators to predict the residual heterogeneity is influenced by different factors, such as the number of studies (Guolo \& Varin, 2017; Panityakul et al., 2013; Hardy \& Thompson, 1996) included and the sample size of the individual studies (Panityakul et al., 2013).
A third, and obvious factor, that is classified as relevant to model performance is heterogeneity among studies being meta-analysed (Kontopantelis \& Reeves, 2011; Jackson \& White, 2018). Coverage from models degrades when the residual heterogeneity increases, mostly when the amount of studies is small (Brockwell \& Gorden, 2001). Considering that all models their performance is linked to the accuracy of the estimate. According to Sidik \& Jonkman (2007), it is generally the case that the larger true between-study variance is, the more biased the estimate can be, which diminishes the performance of the method.

**Methods for estimating residual heterogeneity**
Numerous methods have been proposed to accurately estimate the residual heterogeneity, including the Hedges (HE), DerSimonian–Laird/Method of Moments (DL), Sidik and Jonkman (SJ), Maximum Likelihood (ML), Restricted Maximum Likelihood (REML), and Empirical Bayes (EB) method. These methods are mostly divided into two groups: closed-form or non-iterative methods and iterative methods. The main difference between these groups is that the closed form group uses a predetermined number of steps to provide an estimation for the residual heterogeneity, whereas the iterative methods run multiple iteration, as the name suggests, to converge to a solution when a specific criterion is met. It is important to note that some iterative methods do not produce a solution when they fail to converge after a predetermined amount of iteration.

@@

However, a least squares method could still be somewhat valuable in some situations. It is extremely suitable to estimate a linear relationship. In the case of dichotomous moderators, the relationship is always perfectly linear. A powerful non-linear estimation tool is in the situation of dichotomous moderators unnecessary and would not perform better at all. Whenever a non-linear relation gets fitted on data with an underlying linear relation, it will cause problems when this fit gets used for the prediction of future data. Given the various arguments, this paper provides an approach to tackle this problem of the least squares methods whilst still making use of a linear method. The weighted least squares are replaced with the so-called LASSO regression for the estimation of the regression coefficients. This algorithm shrinks or penalizes the regression coefficients and performs variable selection (James et al., 2013; Hesterberg, Choi, Meier, \& Fraley, 2008).

>>>>

---
title             : "Select relevant moderators in meta-regression using Bayesian penalization"
shorttitle        : "BAYESIAN REGULARIZED META-ANALYSIS"

author:
  - name: "Caspar J. Van Lissa"
    affiliation: "1,2"
    corresponding: yes
    address: "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email: "c.j.vanlissa@uu.nl"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Programming front-end
  - name: "Sara van Erp"
    affiliation: "1"
    role:
      - Writing - Contributions and feedback
      - Programming back-end
affiliation:
  - id            : "1"
    institution   : "Utrecht University, dept. Methodology & Statistics"
  - id            : "2"
    institution   : "Open Science Community Utrecht"

@@

<!--
Skeleton lasso/pema paper
1.) What is Meta-analysis?
2.) What is meta-regression and how does it complement meta-analysis?
	a.) Introduce Moderators
	b.) Study Heterogeneity + Random Sampling Error (and their difference)	
2.5.) Fixed vs. random effects
	a.) Shortcomings of fixed effect models
3.) Shortcomings of current meta regressions w.r.t. estimating coefficients and heterogeneity:
	a.) Small sample size / overfitting
	b.) Non-normal data
4.) Various methods to estimate heterogeneity (and coefficients)
	a.) The use of WLS and REML
5.) Intro to Frequentist linear methods/Bayesian methods and Random forests, along with their 
(dis-)advantages:
	a.) Rma: uses WLS for estimation
	b.) MetaForest (Random Effects): Uses Random Forest Algorithm
	c.) Lasso Pema: uses penalized Lasso
	d.) Horseshoe Pema: uses horseshoe priors
6.) Goal of the current study
7.) Means of attaining goal and evaluation of performance:
	a.) simulation study
	b.) algorithmic performance
	c.) design factors
	d.) Impact of design factors on algorithim performance
	e.) Hypotheses of algorithmic performances

@@

# Introduction
-->

Meta-analysis is a quantitative form of evidence synthesis,
whereby effect sizes from multiple similar studies are aggregated.
In its simplest form, this aggregation consists of the computation of a summary effect as a weighted average of the observed effect sizes.
This average is weighted to account for the fact that some observed effect sizes are assumed to be more informative about the underlying population effect.
Each effect size is assigned a weight that determines how influential it is in calculating the summary effect.
This weight is based on specific assumptions;
for example, the *fixed effect* model assumes that all observed effect sizes reflect one underlying true population effect size.
This assumption is well-suited to the situation where effect sizes from close replication studies are meta-analyzed [@higgins_re-evaluation_2009, fabrigar_conceptualizing_2016, maxwell_is_2015]. 
The *random effects* model, by contrast, assumes that population effect sizes follow a normal distribution.
Each observed effect size provides information about the mean and standard deviation of this distribution of population effect sizes.
This assumption is more appropriate when studies are conceptually similar and differences between them are random [@higgins_re-evaluation_2009, fabrigar_conceptualizing_2016, maxwell_is_2015].

Not all heterogeneity in effect sizes is random, however.
Quantifiable between-study differences may introduce systematic heterogeneity.
Such between-study differences are known as "moderators".
For example, if studies have been replicated in Europe and the Americas, this difference can be captured by a binary moderator called "continent".
Alternatively, if studies have used different dosages of the same drug, this may be captured by a continuous moderator called "dosage".
Systematic heterogeneity in the observed effect sizes can be accounted for using *meta-regression* (Viechtbauer \& López-López, 2015).
This technique provides estimates of the effect of one or more study characteristics on the overall effect size,
as well as of the overall effect size and residual heterogeneity after controlling for their influence.

One common application of meta-analysis is to summarize existing bodies of literature.
In such situations, the number of moderators is often relatively high because similar research questions have been studied in different laboratories,
using different methods, instruments, and samples.
Each of these between-study differences could be coded as a moderator, and some of these moderators may explain systematic heterogeneity.

It is theoretically possible to account for the influence of multiple moderators using meta-regression.
However, like any regression-based approach, meta-regression requires a relatively high number of cases (studies) per parameter obtain sufficient power to examine heterogeneity.
In practice the number of available studies is often too low to examine heterogeneity reliably (Riley, Higgins, & Deeks, 2011).
At the same time, there are many potential sources of heterogeneity,
as similar research questions are studied in different laboratories, using different methods,
instruments, and samples.
This leads to a problem known as the "curse of dimensionality": the number of candidate moderators is large relative to the number of cases in the data.
Such cases do not fit comfortably into the
classic meta-analysis paradigm, which, like any regression-based approach, requires a
high number of cases per parameter. 
Between-studies thus presents a non-trivial challenge to data aggregation
using classic meta-analytic methods.
At the same time, it also offers an unexploited
opportunity to learn which differences between studies have an impact on the effect size
found, if adequate exploratory techniques can be developed.

Addressing the curse of dimensionality necessitates *variable selection*:
the selection of a smaller subset of relevant moderators from a larger number of candidate moderators.
One way to perform variable selection is by relying on theory.
However, in many fields of science, theories exist at the individual level of analysis (e.g., in social science, at the level of individual people).
These theories do not necessarily generalize to the study level of analysis.
Using theories at the individual level for moderator selection at the study level amounts to committing the ecological fallacy: generalizing inferences across levels of analysis [@jargowskyEcologicalFallacy2004].
To illustrate what theory at the study level of analysis might look like, 
consider the so-called *decline effect*.
It is a phenomenon whereby effect sizes in a particular tranche of the literature seem to diminish over time [@schoolerUnpublishedResultsHide2011].
It has been theorized that the decline effect can been attributed to regression to the mean:
A finding initially draws attention from the research community because an anomalously large effect size has been published, and subsequent replications find smaller effect sizes.
Based on the decline effect, we might thus expect the variable "year of publication" to be a relevant moderator of study effect sizes.
Note that this prediction is valid even if year is orthogonal to the outcome of interest within each study.
Until more theory about the drivers of between-study heterogeneity is developed,
however, this approach will have limited utility for variable selection.
<!--A second example that might illustrate this problem is a study that concluded that American college students' empathy had decreased over time, based on meta-analysis of 72 samples collected between 1979 and 2009.-->

An alternative solution is to rely on statistical methods for variable selection.
This is a focal issue in the discipline of machine learning [@hastieElementsStatisticalLearning2009].
One technique that facilitates variable selection is *regularization*:
shrinking model parameters towards zero, such that only larger parameters remain.
Although this technique biases the parameter estimates,
it also reduces their variance, which has the advantage of producing more generalizable results that make better predictions for new data [see @hastieElementsStatisticalLearning2009].
This paper introduces *Bayesian regularized meta-regression* (BRMA),
an algorithm that uses Bayesian estimation with regularizing priors to perform variable selection in meta-analysis.
The algorithm is implemented in the function `brma()` in the R-package `pema`.
<!--
Thus, there is a need of a regularization method to curtail overfitting. Least Absolute Shrinkage and Selection Operator [LASSO] (L1-norm regularization) can fulfill this role, since it has an advantage in terms of feature selection. The goal of this project is to implement L1-norm regularization in the weighted meta-regression, developing an new estimator for regularized meta-regression.
This dilemma could be resolved by an exploratory technique that can identify relevant moderators in meta-analysis,
and which is relatively robust to small sample sizes.
-->
<!--Such shrinkage is advantageous because it performs variable selection and results in a sparse model.
Sparse models are easier to interpret, as fewer non-zero effects remain.
Regularization also provides a solution to the curse of dimensionality; unlike standard regression models, it can provide identified models even if the number of moderators exceeds the number of cases.-->
<!--By doing this it automatically performs variable selection. It does not seem to be immediately clear why shrinking the coefficients should be an improvement to the model. However, by shrinking the parameters, it lowers the variance of the model by increasing the bias only a little bit. In other words, the model sacrifices some of its ability to fit the current data, to greatly increase the ability to predict future data with the same fit (James et al., 2013). This is better known as the bias/variance tradeoff (Briscoe & Feldman, 2011).-->

@@

To understand how BRMA estimates the relevant parameters and performs variable selection, it is instructional to first review the statistical underpinnings of the aforementioned classic approaches to meta-analysis.
First is the fixed-effect model, which assumes that each observed effect size $T_i$ is an estimate of an underlying true effect size $\Theta$ [@hedgesFixedRandomeffectsModels1998].
The only cause of heterogeneity in observed effect sizes is presumed to be effect size-specific sampling variance, $v_i$, which is treated as known, and computed as the square of the standard error of the effect size.
Thus, for a collection of $k$ studies, the observed effects sizes of individual studies $i$ (for $i$ = 1,2, . . . $k$) are given by:

@@

<!--
\begin{aligned}
y_i &= \theta_i + \epsilon_i &\text{where } \epsilon_i \sim N(0, \sigma^2_i)\\ % \text{ and } 
%\theta_1 &= \theta_2 \dots = \theta_k
\end{aligned}-->

Under the fixed effect model, the estimated population effect size  $\hat{\theta}$ is obtained by computing a weighted average of the observed effect sizes.
If sampling error is assumed to be the only source of variance in observed effect size,
then it follows that studies with smaller standard errors estimate the underlying true effect size more precisely<!--(Schmidt, Oh \& Hayes, 2009)-->.
The fixed-effect weights are thus simply the reciprocal of the sampling variance, $w_{i} =  \frac{1}{v_i}$.
The estimate of the true effect is a weighted average across observed effect sizes:

\begin{equation}
\hat{\theta} = \frac{\sum_{i=1}^k w_iT_i}{\sum_{i=1}^k w_i}
\end{equation}
-->
<!--A highly likely consequence is that this will lead to a huge amount of possible moderators (Caserio, 2014). Caused by differences in for example cultures of research populations and used methods or instruments (Neuman, 2011). Even in replication studies there are sometimes moderators that are unanticipated (Kunert, 2016). This leads very often to an eventual poor performance of the fixed-effects meta-analysis model (Snijders, 2005). -->

Whereas the fixed-effect model assumes that only one true population effect exists,
the random-effects model assumes that true effects may vary for unknown reasons,
and thus follow a (normal) distribution of their own (Hedges \& Vevea, 1998).
This heterogeneity of the true effects is represented by their variance, $\tau^{2}$.
The random effect model thus assumes that the heterogeneity in observed effects can be decomposed into sampling error and between-studies heterogeneity, resulting in the following equation for the observed effect sizes:

\begin{align}
T_i &= \Theta + \zeta_{i} + \epsilon_i\\
\text{where } \zeta_i &\sim N(0, \tau^2)\\
\text{and } \epsilon_i &\sim N(0, v_i)
\end{align}

In this model, $\Theta$ is the mean of the distribution of true effect sizes, and $\tau^2$ is its variance, which can be interpreted as the variance between studies.

If the true effect sizes follow a distribution, 
then even less precise studies (with larger sampling errors) may provide some information about this distribution.
Like fixed-effect weights, random effects weights are still influenced by sampling error, but this influence is attenuated by the estimated variance of the true effect sizes. 
The random-effects weights are thus given by $w_{i} =  \frac{1}{v_i + \hat{\tau}^2}$.
It is important to note that,
whereas the sampling error for each individual effect size is treated as known,
between-study heterogeneity $\tau^{2}$ must be estimated.
This estimate is represented by $\hat{\tau}^{2}$.

### Meta-regression

The random effects model assumes that causes of heterogeneity in the true effect sizes are unknown, and that their influence is random.
Oftentimes, however, there are systematic sources of heterogeneity in true effect sizes.
These between-study differences can be coded as moderators, and their influence can be estimated and controlled for using meta-regression.
Meta-regression with $p$ moderators can be expressed with the following equation, where $x_{1\ldots p}$ represent the moderators, and $\beta_{1\ldots p}$ the regression coefficients:

\begin{align}
T_i &= \beta_{0}+ \beta_{1}x_{1}+ \beta_{2}x_{2} + \ldots + \beta_{p}x_{p} + \zeta_{i} + \epsilon_i\\
\end{align}

Note that $\beta_0$ represents the intercept of the distribution of true effect sizes after controlling for the moderators
and the error term $\zeta_{i}$ represents residual between-studies heterogeneity.
This term is still included because unexplained heterogeneity often remains after accounting for the moderators (Thompson \& Sharp, 1999).
This is a mixed-effects model; the intercept and effects of moderators are treated as fixed and the residual heterogeneity as random (Viechtbauer \& López-López, 2015).

<!--
An accurate estimation of the residual heterogeneity contributes to a better interpretation of the effect of the moderators (Panityakul, Bumrungsup \& Knapp, 2013).-->

To solve this model, the regression coefficients and residual heterogeneity must be estimated simultaneously.
<!--The topic of estimating the residual heterogeneity is a highly discussed one (Veroniki et al., 2016; Viechtbauer \& López-López, 2015; Panityakul et al., 2013). The ability of the estimators to predict the residual heterogeneity is influenced by different factors, such as the number of studies (Guolo \& Varin, 2017; Panityakul et al., 2013; Hardy \& Thompson, 1996) included and the sample size of the individual studies (Panityakul et al., 2013).
A third, and obvious factor, that is classified as relevant to model performance is heterogeneity among studies being meta-analysed (Kontopantelis \& Reeves, 2011; Jackson \& White, 2018). Coverage from models degrades when the residual heterogeneity increases, mostly when the amount of studies is small (Brockwell \& Gorden, 2001). Considering that all models their performance is linked to the accuracy of the estimate. According to Sidik \& Jonkman (2007), it is generally the case that the larger true between-study variance is, the more biased the estimate can be, which diminishes the performance of the method.-->
Numerous methods have been proposed to estimate meta-regression models, the most commonly used of which is restricted maximum likelihood (REML).
REML is an iterative method, meaning it performs the same calculations repeatedly, updating the estimated regression coefficients and residual heterogeneity until these estimates stabilize.
<!--, including the Hedges (HE), DerSimonian–Laird/Method of Moments (DL), Sidik and Jonkman (SJ), Maximum Likelihood (ML), Restricted Maximum Likelihood (REML), and Empirical Bayes (EB) method. These methods are mostly divided into two groups: closed-form or non-iterative methods and iterative methods. The main difference between these groups is that the closed form group uses a predetermined number of steps to provide an estimation for the residual heterogeneity, whereas the iterative methods run multiple iteration, as the name suggests, to converge to a solution when a specific criterion is met. It is important to note that some iterative methods do not produce a solution when they fail to converge after a predetermined amount of iteration.-->
In contrast to a regularized analysis technique, this estimator produces low bias, which means that the average value of the estimated regression coefficients and residual heterogeneity is close to their true values (Panityakul et al., 2013; Hardy & Thompson, 1996).
<!--It needs a starting estimation of $\tau^{2}$, which is usually estimated by one of the non-iterative methods (Viechtbauer \& López-López, 2015). Besides the starting value of $\tau^{2}$, it needs in every iteration an estimation of the regression coefficients of the moderators. These are typically estimated by using the Weighted Least Squares (WLS) method. This is a variation of the Ordinary Least Squares (OLS), but in the case of meta-analysis it is necessary to assess weights to the coefficients. In systematic reviews large variation in standard errors is often observed, which will result in large heteroscedasticity in the estimation of the effects (Stanley \& Doucouliagos, 2017). The addition of weights is a way to adjust for this heteroscedasticity. The weights are formulated as presented in equation (5).-->
<!--

However, a least squares method could still be somewhat valuable in some situations. It is extremely suitable to estimate a linear relationship. In the case of dichotomous moderators, the relationship is always perfectly linear. A powerful non-linear estimation tool is in the situation of dichotomous moderators unnecessary and would not perform better at all. Whenever a non-linear relation gets fitted on data with an underlying linear relation, it will cause problems when this fit gets used for the prediction of future data. Given the various arguments, this paper provides an approach to tackle this problem of the least squares methods whilst still making use of a linear method. The weighted least squares are replaced with the so-called LASSO regression for the estimation of the regression coefficients. This algorithm shrinks or penalizes the regression coefficients and performs variable selection (James et al., 2013; Hesterberg, Choi, Meier, \& Fraley, 2008).-->

### Regularized regression

Regularized regression biases parameter estimates towards zero by including a shrinkage penalty in the estimation process.
Before examining the Bayesian case, we will explain the principle using frequentist OLS regression as an example.
OLS regression estimates the model parameters by minimizing the Residual Sum of Squares (RSS) of the dependent variable, which is given by:

$$
RSS=\sum_{i=1}^{n}(y_{i} - \beta_{0} - \sum_{j=1}^{p}\beta_{j}x_{ij})^2
$$
The resulting parameter estimates are those that give the best predictions of the dependent variable in the present dataset.
Penalized regression, by contrast, adds a penalty term to the quantity to be minimized.
One commonly used penalty is the L1-norm of the regression coefficients, or LASSO penalty,
which corresponds to the sum of their absolute values.
This gives the penalized residual sum of squares:

$$
PRSS= RSS + \lambda \sum_{j=1}^{p}|\beta_{j}|
$$

Where $\lambda$ is a tuning parameter that determines how influential the penalty term will be.
If $\lambda$ is zero, the shrinkage penalty has no impact at all and the penalized regression will produce the OLS estimates.
If $\lambda \to \infty$, all coefficient shrink towards zero, producing the null model.
<!--Another commonly used penalty is the L2-norm of the coefficients, or ridge penalty,
which corresponds to the sum of their squared values: $\sum_{j=1}^{p}\beta_{j}^2$.-->
Because the penalty term is a function of the regression coefficients,
the optimizer has an incentive to keep the regression coefficients as small as possible.
<!--The LASSO penalty has the unique property of shrinking some coefficients to be exactly zero,
but the ridge penalty does not do so, as -->
Note that theLASSO penalty is but one example of a shrinkage penalty; other penalties exist, with some unique properties.

<!--The Lasso shrinkage method is not the only shrinkage method, there do exist some others. Nevertheless, the lasso is in the case the best option. It possesses, as opposed to other methods, the ability to shrink the parameter not towards zero, but to be exactly zero (James et al., 2013; Hesterberg, Choi, Meier, \& Fraley, 2008). This means that the lasso can perform variable selection, something that is specifically aimed for in this study. -->

<!--
**Alternative to linear model: Tree Based models**
An alternative that can perform variable selection, are tree-based models. These kinds of models have numerous other advantages over linear models. Tree-based models can be used for any data type, are easy to represent visually, require little data preparation and got larger power than linear regressions when moderators exceed observations in quantity. They are also more flexible in handling moderator interactions and non-linearity. As a result of that, they are better in modelling the complicated nature of human behaviour (Earp \& Trafimow, 2015). Decision trees split from the top down and group data in so-called ‘sub-nodes’, in which the data’s aspects are most homogeneous. The goal is to split to get the sub-nodes as uniform as possible, which can be until fully homogenous groups, or if a pre-specified touchstone is reached. 
Still, singletree based models have some limitations. First of all, tree models are unstable, small fluctuations that are utilized to make the model have a possibility to lead to considerable alterations in the constructions of the tree (Dwyer \& Holte, 2007). Second, it has problems with seizing linearity, because it only makes ‘twofold splits’ (Steyerberg, 2019). At last, tree-based models are susceptible to overfitting (Hastie et al, 2009).

The study displayed also other advantages from random forests over singletrees. It had greater power, was able to make better predictions, gave estimates of the cross-validation error and yielded useful measures of variable importance and partial prediction plots (van Lissa, 2017). MetaForest can at the moment be considered as the best working technique to explore heterogeneity in meta-analysis. In van Lissa (2017), that only presented estimates of $\tau^{2}$ based on the raw data, we saw that MetaForest had certain robustness against a low number of studies. If moderators were continuously distributed, MetaForest had sufficient power at approximately 20 studies. However, there is an important feature to prove before we can make such an assumption. The underlying data generating models in the two simulation studies of van Lissa (2017) only included normal distributed moderators. Renouncing from normal distributions may affect the performance of the model, but since normal distribution in real-life data is more an exception than a normal state of affairs (Micceri, 1989), it is entirely possible that procedures are affected by skewness, leverage, balance etc. It is important to know how MetaForest performs in these kinds of situations.-->

### Bayesian estimation

<!--To solve this model, the moderator coefficients and the residual heterogeneity must be estimated simulataneously.
<!--The topic of estimating the residual heterogeneity is a highly discussed one (Veroniki et al., 2016; Viechtbauer \& López-López, 2015; Panityakul et al., 2013). The ability of the estimators to predict the residual heterogeneity is influenced by different factors, such as the number of studies (Guolo \& Varin, 2017; Panityakul et al., 2013; Hardy \& Thompson, 1996) included and the sample size of the individual studies (Panityakul et al., 2013).
A third, and obvious factor, that is classified as relevant to model performance is heterogeneity among studies being meta-analysed (Kontopantelis \& Reeves, 2011; Jackson \& White, 2018). Coverage from models degrades when the residual heterogeneity increases, mostly when the amount of studies is small (Brockwell \& Gorden, 2001). Considering that all models their performance is linked to the accuracy of the estimate. According to Sidik \& Jonkman (2007), it is generally the case that the larger true between-study variance is, the more biased the estimate can be, which diminishes the performance of the method.-->
<!--Numerous methods have been proposed to accurately estimate the residual heterogeneity, including the Hedges (HE), DerSimonian–Laird/Method of Moments (DL), Sidik and Jonkman (SJ), Maximum Likelihood (ML), Restricted Maximum Likelihood (REML), and Empirical Bayes (EB) method. These methods are mostly divided into two groups: closed-form or non-iterative methods and iterative methods. The main difference between these groups is that the closed form group uses a predetermined number of steps to provide an estimation for the residual heterogeneity, whereas the iterative methods run multiple iteration, as the name suggests, to converge to a solution when a specific criterion is met. It is important to note that some iterative methods do not produce a solution when they fail to converge after a predetermined amount of iteration.

@@

However, a least squares method could still be somewhat valuable in some situations. It is extremely suitable to estimate a linear relationship. In the case of dichotomous moderators, the relationship is always perfectly linear. A powerful non-linear estimation tool is in the situation of dichotomous moderators unnecessary and would not perform better at all. Whenever a non-linear relation gets fitted on data with an underlying linear relation, it will cause problems when this fit gets used for the prediction of future data. Given the various arguments, this paper provides an approach to tackle this problem of the least squares methods whilst still making use of a linear method. The weighted least squares are replaced with the so-called LASSO regression for the estimation of the regression coefficients. This algorithm shrinks or penalizes the regression coefficients and performs variable selection (James et al., 2013; Hesterberg, Choi, Meier, \& Fraley, 2008). -->
